Revisions Analyses & Figures

### 2023-10-18 Revisions_Analyses&Figures.Rmd
Updated file for paper revisions - added longitudinal analyses, updated figures and tables. Added relevant demographics, figures, and tables for new follow-up model.

@@

@@

## from model code

@@

vip(abcd_model_obj_combat, num_features = 175)

vip(abcd_model_obj_combat, num_features = 20)

vi_updated <- vi(abcd_model_obj_combat)

@@

vi_updated2 <- vi(extract_fit_parsnip(fit_workflow_combat))

#vi_model(abcd_model_obj_combat)

# ggseg importance plots
# Rename columns to fit with ggseg atlas (ugghhh)

@@

abcd_vi <- left_join(vi(abcd_model_obj_combat), abcd_vi_renamed)

@@

ggplot(dk_vi_vol) +
  geom_brain(atlas = dk, position = position_brain(hemi ~ side), aes(fill = Importance))+
  theme_void() +
  scale_fill_gradient(low = '#FDD872', high = '#E76F51') +
  labs(title = "Cortical Volume")
ggsave(filename="abcd_model_dk_vol_importance.png",
                         width=8, height=4, units='in', dpi=300)

@@

ggplot(dk_vi_area) +
  geom_brain(atlas = dk, position = position_brain(hemi ~ side), aes(fill = Importance))+
  theme_void() +
  scale_fill_gradient(low = '#FDD872', high = '#E76F51') +
  labs(title = "Cortical Area")
ggsave(filename="abcd_model_dk_area_importance.png",
                         width=8, height=4, units='in', dpi=300)

#Subcortical
aseg_vi <- abcd_vi_renamed %>%
  filter(label != "") %>% 
  select(Importance,label)

@@

ggplot(aseg_vi) +
  geom_brain(atlas = aseg, side="coronal", aes(fill = Importance))+
  theme_void() +
  scale_fill_gradient(low = '#FDD872', high = '#E76F51')
ggsave(filename="abcd_model_aseg_importance_coronal.png",
                          width=7, height=4, units='in', dpi=300)

ggplot(aseg_vi) +
  geom_brain(atlas = aseg, side="sagittal", aes(fill = Importance))+
  theme_void() +
  scale_fill_gradient(low = '#FDD872', high = '#E76F51')
ggsave(filename="abcd_model_aseg_importance_sagittal.png",
                          width=7, height=4, units='in', dpi=300)

@@

load("~/Documents/FYP/abcd_brainage_pds_followup_combat.Rda")

@@

# maybe make a table of results
```{r}

@@

# Followup - Model 2
standardize_parameters(followup_puberty_y_mod2)
standardize_parameters(followup_puberty_p_mod2)
standardize(followup_puberty_p_mod2)
```

@@

summary(lm.beta(followup_puberty_y_mod2))
```

@@

describe(abcd_brainage_pds_followup_combat)
```
# New Demographics Column for Follow- Up (Model 2)
```{r}
nrow(abcd_brainage_pds_followup_combat %>% filter(sex == "F")) / nrow(abcd_brainage_pds_followup_combat)
nrow(abcd_brainage_pds_followup_combat %>% filter(sex == "M")) / nrow(abcd_brainage_pds_followup_combat)

demographics_baseline_abcdmodel <- left_join(abcd_baseline, demographics)

@@

@@

#family income
table(demographics_baseline$demo_comb_income_v2)

#Overall values
#Non-hispanic white
demographics_baseline %>% 
  filter(demo_race_a_p___10 == 1 & demo_race_a_p___11 != 1 & demo_race_a_p___12 != 1 & demo_race_a_p___13 != 1 & demo_race_a_p___14 != 1 & demo_race_a_p___15 != 1 & demo_race_a_p___16 != 1 & demo_race_a_p___17 != 1 & demo_race_a_p___18 != 1 & demo_race_a_p___19 != 1 & demo_race_a_p___20 != 1 & demo_race_a_p___21 != 1 & demo_race_a_p___22 != 1 & demo_race_a_p___23 != 1 & demo_race_a_p___24 != 1 & demo_race_a_p___25 != 1 & demo_ethn_v2 != 1)

#Non-hispanic Black
demographics_baseline %>% 
  filter(demo_race_a_p___10 != 1 & demo_race_a_p___11 == 1 & demo_race_a_p___12 != 1 & demo_race_a_p___13 != 1 & demo_race_a_p___14 != 1 & demo_race_a_p___15 != 1 & demo_race_a_p___16 != 1 & demo_race_a_p___17 != 1 & demo_race_a_p___18 != 1 & demo_race_a_p___19 != 1 & demo_race_a_p___20 != 1 & demo_race_a_p___21 != 1 & demo_race_a_p___22 != 1 & demo_race_a_p___23 != 1 & demo_race_a_p___24 != 1 & demo_race_a_p___25 != 1 & demo_ethn_v2 != 1)

#Hispanic
demographics_baseline %>% 
  filter(demo_ethn_v2 == 1)

demographics_baseline %>% 
  filter(((demo_race_a_p___10 == 1 | demo_race_a_p___11 == 1) & demo_race_a_p___12 != 1 & demo_race_a_p___13 != 1 & demo_race_a_p___14 != 1 & demo_race_a_p___15 != 1 & demo_race_a_p___16 != 1 & demo_race_a_p___17 != 1 & demo_race_a_p___18 != 1 & demo_race_a_p___19 != 1 & demo_race_a_p___20 != 1 & demo_race_a_p___21 != 1 & demo_race_a_p___22 != 1 & demo_race_a_p___23 != 1 & demo_race_a_p___24 != 1 & demo_race_a_p___25 != 1) & demo_ethn_v2 == 1)

#Asian
demographics_baseline %>% 
  filter(demo_race_a_p___10 != 1 & demo_race_a_p___11 != 1 & demo_race_a_p___12 != 1 & demo_race_a_p___13 != 1 & demo_race_a_p___14 != 1 & demo_race_a_p___15 != 1 & demo_race_a_p___16 != 1 & demo_race_a_p___17 != 1 & ( demo_race_a_p___18 == 1 | demo_race_a_p___19 == 1 | demo_race_a_p___20 == 1 | demo_race_a_p___21 == 1 | demo_race_a_p___22 == 1 | demo_race_a_p___23 == 1 | demo_race_a_p___24 == 1) & demo_race_a_p___25 != 1 & demo_ethn_v2 != 1)

#Native American Alaska Native
demographics_baseline %>% 
  filter(demo_race_a_p___10 != 1 & demo_race_a_p___11 != 1 & (demo_race_a_p___12 ==1 | demo_race_a_p___13 == 1) & demo_race_a_p___14 != 1 & demo_race_a_p___15 != 1 & demo_race_a_p___16 != 1 & demo_race_a_p___17 != 1 & demo_race_a_p___18 != 1 & demo_race_a_p___19 != 1 & demo_race_a_p___20 != 1 & demo_race_a_p___21 != 1 & demo_race_a_p___22 != 1 & demo_race_a_p___23 != 1 & demo_race_a_p___24 != 1 & demo_race_a_p___25 != 1 )

@@

demographics_baseline %>% 
  mutate_at(c(18:33), as.numeric) %>% 
  mutate(
    demo_race_asian = case_when((demo_race_a_p___18 == 1 | demo_race_a_p___19 == 1 | demo_race_a_p___20 == 1 | demo_race_a_p___21 == 1 | demo_race_a_p___22 == 1 | demo_race_a_p___23 == 1 | demo_race_a_p___24 == 1) ~ 1,
                            (demo_race_a_p___18 != 1 & demo_race_a_p___19 != 1 & demo_race_a_p___20 != 1 & demo_race_a_p___21 != 1 & demo_race_a_p___22 != 1 & demo_race_a_p___23 != 1 & demo_race_a_p___24 != 1) ~ 0),
         demo_race_native_american_alaskan = case_when((demo_race_a_p___12 ==1 | demo_race_a_p___13 == 1) ~ 1,
                                                       (demo_race_a_p___12 !=1 & demo_race_a_p___13 != 1) ~ 0),
         race_total = rowSums(across(c(demo_race_a_p___10, demo_race_a_p___11, demo_race_a_p___14, demo_race_a_p___15, demo_race_a_p___16, demo_race_a_p___17, demo_race_a_p___25, demo_race_asian, demo_race_native_american_alaskan)), na.rm=T)) %>% 
  filter(race_total > 1)

@@

@@

# sex differences
```{r}
# model with sex as covariate?

@@

# Fig 1 with line of identity, jitter fixed
```{r}
# fig 1 has different jitter for ab vs. cd. x axis scaling of ab and cd should be equal
# add line of identity to fig 1 to vizualize bias - already done for AB, but CD has a regression line, do they want a 1:1 line on that too?
```

@@

# change colors
# decide if it should only show the same participants
```
# Plot of model 1 & 2 prediction overlaid (followup)
```{r}
# overlay model 1 on new predictions in fig 4

@@

ggplot(both_mods_followup, aes(x=truth, y=corrected_pred, group=model, col=model, fill=model)) +
  geom_jitter(alpha=.2) +
  scale_color_manual(values = c("#619B8A", "#856088")) +
  #geom_abline(a=0, b=1, color='#233D4D') +
  #xlim(8, 15) + # 5, 20
 # ylim(8, 15) +
  #geom_smooth(method=lm, color='#233D4D') +
  labs(x = "Scan/Chronological Age", y ="Predicted Age") +
  theme_classic() + 
  theme(text = element_text(size = 14))

# change colors
# decide if it should only show the same participants
```

@@

```
```{r}

####### UPDATE COLORS

@@

```{r}
# Prediction Plots

```{r}
# Model feature - baseline

# vip

@@

# vip
abcd_model_obj_combat_followup <- fit_workflow_combat_followup$fit$fit$fit

@@

vip(abcd_model_obj_combat_followup, num_features = 20)

vi(fit_workflow_combat_followup$fit$fit$fit)

@@

abcd_vi_followup <- left_join(vi(abcd_model_obj_combat_followup), abcd_vi_renamed)

@@

abcd_vi_dk_followup <- left_join(vi(abcd_model_obj_combat_followup), abcd_vi_renamed_dk)

@@

ggplot(dk_vi_vol_followup) +
  geom_brain(atlas = dk, position = position_brain(hemi ~ side), aes(fill = Importance))+
  theme_void() +
  scale_fill_gradient(low = '#FDD872', high = '#E76F51') +
  labs(title = "Cortical Volume")
ggsave(filename="abcd_model_dk_vol_importance.png",
                         width=8, height=4, units='in', dpi=300)

@@

ggplot(dk_vi_area_followup) +
  geom_brain(atlas = dk, position = position_brain(hemi ~ side), aes(fill = Importance))+
  theme_void() +
  scale_fill_gradient(low = '#FDD872', high = '#E76F51') +
  labs(title = "Cortical Area")
ggsave(filename="abcd_model_dk_area_importance.png",
                         width=8, height=4, units='in', dpi=300)

@@

ggplot(aseg_vi_followup) +
  geom_brain(atlas = aseg, side="coronal", aes(fill = Importance))+
  theme_void() +
  scale_fill_gradient(low = '#FDD872', high = '#E76F51')
ggsave(filename="abcd_model_aseg_importance_coronal.png",
                          width=7, height=4, units='in', dpi=300)

ggplot(aseg_vi_followup) +
  geom_brain(atlas = aseg, side="sagittal", aes(fill = Importance))+
  theme_void() +
  scale_fill_gradient(low = '#FDD872', high = '#E76F51')
ggsave(filename="abcd_model_aseg_importance_sagittal.png",
                          width=7, height=4, units='in', dpi=300)

@@

```{r}
# correlation between gaps from waves, or something more complicated?
# maybe multilevel model so that it's nested by participant? -

>>>>

Load everything (corrected)
```{r}
load("~/Documents/FYP/Revisions/abcd_brainage_pds_baseline_combat.Rda")
load("~/Documents/FYP/Revisions/abcd_brainage_pds_followup_combat.Rda")

load("~/Documents/FYP/Revisions/brainage_pds_baseline_combat.Rda")
load("~/Documents/FYP/Revisions/brainage_pds_followup_combat.Rda")

@@

# fit metrics
```{r}
abcd_brainage_pds_followup_combat %>%
  metrics(truth = truth, estimate = .pred)

abcd_brainage_pds_followup_combat %>%
  metrics(truth = truth, estimate = corrected_pred)

cor(abcd_brainage_pds_followup_combat$truth, abcd_brainage_pds_followup_combat$corrected_gap)
```

@@

## testing
load("~/Documents/FYP/UpdatedModels/fit_workflow_combat.rds")
#model_obj <- xgb.load("~/Documents/FYP/UpdatedModels/abcd_model_obj_combat")
#model_obj_indexed <- fit_workflow_combat$fit$fit$fit

colnames(df_train)[!(colnames(df_train) %in% vi(fit_workflow_combat)$Variable)]

#xgb.importance(extract_fit_parsnip(fit_workflow_combat))
#xgb.importance(model = model_obj)
#xgb.importance(model = model_obj_indexed)

#xgb.plot.importance(xgb.importance(model = model_obj))

vip(fit_workflow_combat, num_features=20) +
  theme_light()
ggsave(filename="model2_vip_baseline.png",
                          width=7, height=4, units='in', dpi=300)

load("~/Documents/FYP/Revisions/fit_workflow_combat_followup.rds")
#model_obj_followup <- xgb.load("~/Documents/FYP/Revisions/abcd_model_obj_combat_followup")
#model_obj_indexed_followup <- fit_workflow_combat_followup$fit$fit$fit

vi(fit_workflow_combat_followup)

vip(fit_workflow_combat_followup, num_features=20) +
  theme_light()
ggsave(filename="model2_vip_followup.png",
                          width=7, height=4, units='in', dpi=300)
## from model code

@@

#vip(abcd_model_obj_combat, num_features = 175) 
#vip(abcd_model_obj_combat, num_features = 20) 
#vi_updated <- vi(abcd_model_obj_combat)
#vi(fit_workflow_combat)
#vi(fit_workflow_combat, method = "shap")

@@

#vi(fit_workflow_combat$fit$fit)
#vi(fit_workflow_combat$fit$fit$fit)

vi_updated <- vi(extract_fit_parsnip(fit_workflow_combat)) # this seems to work!

vip(extract_fit_parsnip(fit_workflow_combat), num_features = 20)

ggseg importance plots
```{r}
# ggseg importance plots
# Rename columns to fit with ggseg atlas

@@

#abcd_vi <- left_join(vi(abcd_model_obj_combat), abcd_vi_renamed)
abcd_vi <- left_join(vi_updated, abcd_vi_renamed)

@@

ggplot(dk_vi_vol) +
  geom_brain(atlas = dk, position = position_brain(hemi ~ side), aes(fill = Importance))+
  theme_void() +
  scale_fill_gradient(low = '#FDD872', high = '#E76F51') +
  labs(title = "Cortical Volume")
ggsave(filename="abcd_model_dk_vol_importance_combat.png",
                         width=8, height=4, units='in', dpi=300)

@@

ggplot(dk_vi_area) +
  geom_brain(atlas = dk, position = position_brain(hemi ~ side), aes(fill = Importance))+
  theme_void() +
  scale_fill_gradient(low = '#FDD872', high = '#E76F51') +
  labs(title = "Cortical Area")
ggsave(filename="abcd_model_dk_area_importance_combat.png",
                         width=8, height=4, units='in', dpi=300)

#Subcortical
aseg_vi <- abcd_vi %>%
  filter(label != "") %>% 
  select(Importance,label)

@@

ggplot(aseg_vi) +
  geom_brain(atlas = aseg, side="coronal", aes(fill = Importance))+
  theme_void() +
  scale_fill_gradient(low = '#FDD872', high = '#E76F51')
ggsave(filename="abcd_model_aseg_importance_coronal_combat.png",
                          width=7, height=4, units='in', dpi=300)

ggplot(aseg_vi) +
  geom_brain(atlas = aseg, side="sagittal", aes(fill = Importance))+
  theme_void() +
  scale_fill_gradient(low = '#FDD872', high = '#E76F51')
ggsave(filename="abcd_model_aseg_importance_sagittal_combat.png",
                          width=7, height=4, units='in', dpi=300)

@@

@@

# Table of results
```{r}

apa.reg.table(baseline_puberty_y_mod1, filename= "apa_baseline_puberty_y_mod1.doc", table.number = 3)
apa.reg.table(baseline_puberty_p_mod1, filename= "apa_baseline_puberty_p_mod1.doc", table.number = 4)
apa.reg.table(baseline_cognition_mod1, filename= "apa_baseline_cognition_mod1.doc", table.number = 5)

apa.reg.table(followup_puberty_y_mod1, filename= "apa_followup_puberty_y_mod1.doc", table.number = 6)
apa.reg.table(followup_puberty_p_mod1, filename= "apa_followup_puberty_p_mod1.doc", table.number = 7)

apa.reg.table(baseline_puberty_y_mod2, filename= "apa_baseline_puberty_y_mod2.doc", table.number = 8)
apa.reg.table(baseline_puberty_p_mod2, filename= "apa_baseline_puberty_p_mod2.doc", table.number = 9)
apa.reg.table(baseline_cognition_mod2, filename= "apa_baseline_cognition_mod2.doc", table.number = 10)

apa.reg.table(followup_puberty_y_mod2, filename= "apa_followup_puberty_y_mod2.doc", table.number = 11)
apa.reg.table(followup_puberty_p_mod2, filename= "apa_followup_puberty_p_mod2.doc", table.number = 12)

apa.reg.table(baseline_puberty_y_mod1,baseline_puberty_p_mod1, baseline_cognition_mod1,  filename= "apa_baseline_mod1.doc", table.number = 3)

@@

# Followup - Model 2
standardize_parameters(followup_puberty_y_mod2)
standardize_parameters(followup_puberty_p_mod2)
standardize(followup_puberty_p_mod2)

@@

summary(lm.beta(followup_puberty_y_mod2))

apa.reg.table(lm.beta(followup_puberty_y_mod2))

apa.reg.table(followup_puberty_y_mod2, filename= "apa_followup_puberty_y_mod2.doc", table.number = 1)
```

@@

describe(abcd_brainage_pds_followup_combat)
```

# recalculate demographics table
```{r}
demographics_baseline <- left_join(brainage_pds_baseline_combat, demographics)

demographics_followup <- left_join(brainage_pds_followup_combat, demographics)

demographics_baseline_abcdmodel <- left_join(abcd_brainage_pds_baseline_combat, demographics)

@@

demographics_baseline <- left_join(demographics_baseline, demographics_long %>% filter(eventname == "baseline_year_1_arm_1"))

demographics_followup <- left_join(demographics_followup, demographics_long %>% filter(eventname == "2_year_follow_up_y_arm_1"))

@@

demographics_baseline_abcdmodel %>% 
  filter(demo_race_a_p___10 != 1 & demo_race_a_p___11 != 1 & demo_race_a_p___12 != 1 & demo_race_a_p___13 != 1 & (demo_race_a_p___14 == 1 | demo_race_a_p___15 == 1 | demo_race_a_p___16 == 1 | demo_race_a_p___17 == 1 | demo_race_a_p___25 == 1) & demo_race_a_p___18 != 1 & demo_race_a_p___19 != 1 & demo_race_a_p___20 != 1 & demo_race_a_p___21 != 1 & demo_race_a_p___22 != 1 & demo_race_a_p___23 != 1 & demo_race_a_p___24 != 1)
```
# Baseline (model 2)
```{r}
#Overall values
#Non-hispanic white
demographics_baseline_abcdmodel %>% 
  filter(demo_race_a_p___10 == 1 & demo_race_a_p___11 != 1 & demo_race_a_p___12 != 1 & demo_race_a_p___13 != 1 & demo_race_a_p___14 != 1 & demo_race_a_p___15 != 1 & demo_race_a_p___16 != 1 & demo_race_a_p___17 != 1 & demo_race_a_p___18 != 1 & demo_race_a_p___19 != 1 & demo_race_a_p___20 != 1 & demo_race_a_p___21 != 1 & demo_race_a_p___22 != 1 & demo_race_a_p___23 != 1 & demo_race_a_p___24 != 1 & demo_race_a_p___25 != 1 & demo_ethn_v2 != 1)

#Non-hispanic Black
demographics_baseline_abcdmodel %>% 
  filter(demo_race_a_p___10 != 1 & demo_race_a_p___11 == 1 & demo_race_a_p___12 != 1 & demo_race_a_p___13 != 1 & demo_race_a_p___14 != 1 & demo_race_a_p___15 != 1 & demo_race_a_p___16 != 1 & demo_race_a_p___17 != 1 & demo_race_a_p___18 != 1 & demo_race_a_p___19 != 1 & demo_race_a_p___20 != 1 & demo_race_a_p___21 != 1 & demo_race_a_p___22 != 1 & demo_race_a_p___23 != 1 & demo_race_a_p___24 != 1 & demo_race_a_p___25 != 1 & demo_ethn_v2 != 1)

#Hispanic
demographics_baseline_abcdmodel %>% 
  filter(demo_ethn_v2 == 1)

demographics_baseline_abcdmodel %>% 
  filter(((demo_race_a_p___10 == 1 | demo_race_a_p___11 == 1) & demo_race_a_p___12 != 1 & demo_race_a_p___13 != 1 & demo_race_a_p___14 != 1 & demo_race_a_p___15 != 1 & demo_race_a_p___16 != 1 & demo_race_a_p___17 != 1 & demo_race_a_p___18 != 1 & demo_race_a_p___19 != 1 & demo_race_a_p___20 != 1 & demo_race_a_p___21 != 1 & demo_race_a_p___22 != 1 & demo_race_a_p___23 != 1 & demo_race_a_p___24 != 1 & demo_race_a_p___25 != 1) & demo_ethn_v2 == 1)

#Asian
demographics_baseline_abcdmodel %>% 
  filter(demo_race_a_p___10 != 1 & demo_race_a_p___11 != 1 & demo_race_a_p___12 != 1 & demo_race_a_p___13 != 1 & demo_race_a_p___14 != 1 & demo_race_a_p___15 != 1 & demo_race_a_p___16 != 1 & demo_race_a_p___17 != 1 & ( demo_race_a_p___18 == 1 | demo_race_a_p___19 == 1 | demo_race_a_p___20 == 1 | demo_race_a_p___21 == 1 | demo_race_a_p___22 == 1 | demo_race_a_p___23 == 1 | demo_race_a_p___24 == 1) & demo_race_a_p___25 != 1 & demo_ethn_v2 != 1)

#Native American Alaska Native
demographics_baseline_abcdmodel %>% 
  filter(demo_race_a_p___10 != 1 & demo_race_a_p___11 != 1 & (demo_race_a_p___12 ==1 | demo_race_a_p___13 == 1) & demo_race_a_p___14 != 1 & demo_race_a_p___15 != 1 & demo_race_a_p___16 != 1 & demo_race_a_p___17 != 1 & demo_race_a_p___18 != 1 & demo_race_a_p___19 != 1 & demo_race_a_p___20 != 1 & demo_race_a_p___21 != 1 & demo_race_a_p___22 != 1 & demo_race_a_p___23 != 1 & demo_race_a_p___24 != 1 & demo_race_a_p___25 != 1 )

@@

demographics_baseline_abcdmodel %>% 
  mutate_at(c(12:33), as.numeric) %>% 
  mutate(
    demo_race_asian = case_when((demo_race_a_p___18 == 1 | demo_race_a_p___19 == 1 | demo_race_a_p___20 == 1 | demo_race_a_p___21 == 1 | demo_race_a_p___22 == 1 | demo_race_a_p___23 == 1 | demo_race_a_p___24 == 1) ~ 1,
                            (demo_race_a_p___18 != 1 & demo_race_a_p___19 != 1 & demo_race_a_p___20 != 1 & demo_race_a_p___21 != 1 & demo_race_a_p___22 != 1 & demo_race_a_p___23 != 1 & demo_race_a_p___24 != 1) ~ 0),
         demo_race_native_american_alaskan = case_when((demo_race_a_p___12 ==1 | demo_race_a_p___13 == 1) ~ 1,
                                                       (demo_race_a_p___12 !=1 & demo_race_a_p___13 != 1) ~ 0),
         race_total = rowSums(across(c(demo_race_a_p___10, demo_race_a_p___11, demo_race_a_p___14, demo_race_a_p___15, demo_race_a_p___16, demo_race_a_p___17, demo_race_a_p___25, demo_race_asian, demo_race_native_american_alaskan)), na.rm=T)) %>% 
  filter(race_total > 1)

@@

demographics_baseline_abcdmodel %>% 
  filter(demo_race_a_p___10 != 1 & demo_race_a_p___11 != 1 & demo_race_a_p___12 != 1 & demo_race_a_p___13 != 1 & (demo_race_a_p___14 == 1 | demo_race_a_p___15 == 1 | demo_race_a_p___16 == 1 | demo_race_a_p___17 == 1 | demo_race_a_p___25 == 1) & demo_race_a_p___18 != 1 & demo_race_a_p___19 != 1 & demo_race_a_p___20 != 1 & demo_race_a_p___21 != 1 & demo_race_a_p___22 != 1 & demo_race_a_p___23 != 1 & demo_race_a_p___24 != 1)

demographics_followup_abcdmodel %>% 
  filter(demo_race_a_p___10 != 1 & demo_race_a_p___11 != 1 & demo_race_a_p___12 != 1 & demo_race_a_p___13 != 1 & (demo_race_a_p___14 == 1 | demo_race_a_p___15 == 1 | demo_race_a_p___16 == 1 | demo_race_a_p___17 == 1 | demo_race_a_p___25 == 1) & demo_race_a_p___18 != 1 & demo_race_a_p___19 != 1 & demo_race_a_p___20 != 1 & demo_race_a_p___21 != 1 & demo_race_a_p___22 != 1 & demo_race_a_p___23 != 1 & demo_race_a_p___24 != 1)

@@

demographics_followup %>% 
  filter(demo_race_a_p___10 != 1 & demo_race_a_p___11 != 1 & demo_race_a_p___12 != 1 & demo_race_a_p___13 != 1 & (demo_race_a_p___14 == 1 | demo_race_a_p___15 == 1 | demo_race_a_p___16 == 1 | demo_race_a_p___17 == 1 | demo_race_a_p___25 == 1) & demo_race_a_p___18 != 1 & demo_race_a_p___19 != 1 & demo_race_a_p___20 != 1 & demo_race_a_p___21 != 1 & demo_race_a_p___22 != 1 & demo_race_a_p___23 != 1 & demo_race_a_p___24 != 1)
```

# New Demographics Column for Follow- Up (Model 2)
```{r}
nrow(abcd_brainage_pds_followup_combat %>% filter(sex == "F")) / nrow(abcd_brainage_pds_followup_combat)
nrow(abcd_brainage_pds_followup_combat %>% filter(sex == "M")) / nrow(abcd_brainage_pds_followup_combat)

demographics_followup_abcdmodel <- left_join(abcd_brainage_pds_followup_combat, demographics)

demographics_followup_abcdmodel <- left_join(demographics_followup_abcdmodel, demographics_long %>% filter(eventname == "2_year_follow_up_y_arm_1"))

#family income
table(demographics_followup_abcdmodel$demo_comb_income_v2)
# /3693 for %

#Overall values
#Non-hispanic white
demographics_followup_abcdmodel %>% 
  filter(demo_race_a_p___10 == 1 & demo_race_a_p___11 != 1 & demo_race_a_p___12 != 1 & demo_race_a_p___13 != 1 & demo_race_a_p___14 != 1 & demo_race_a_p___15 != 1 & demo_race_a_p___16 != 1 & demo_race_a_p___17 != 1 & demo_race_a_p___18 != 1 & demo_race_a_p___19 != 1 & demo_race_a_p___20 != 1 & demo_race_a_p___21 != 1 & demo_race_a_p___22 != 1 & demo_race_a_p___23 != 1 & demo_race_a_p___24 != 1 & demo_race_a_p___25 != 1 & demo_ethn_v2 != 1)

#Non-hispanic Black
demographics_followup_abcdmodel %>% 
  filter(demo_race_a_p___10 != 1 & demo_race_a_p___11 == 1 & demo_race_a_p___12 != 1 & demo_race_a_p___13 != 1 & demo_race_a_p___14 != 1 & demo_race_a_p___15 != 1 & demo_race_a_p___16 != 1 & demo_race_a_p___17 != 1 & demo_race_a_p___18 != 1 & demo_race_a_p___19 != 1 & demo_race_a_p___20 != 1 & demo_race_a_p___21 != 1 & demo_race_a_p___22 != 1 & demo_race_a_p___23 != 1 & demo_race_a_p___24 != 1 & demo_race_a_p___25 != 1 & demo_ethn_v2 != 1)

#Hispanic
demographics_followup_abcdmodel %>% 
  filter(demo_ethn_v2 == 1)

demographics_followup_abcdmodel %>% 
  filter(((demo_race_a_p___10 == 1 | demo_race_a_p___11 == 1) & demo_race_a_p___12 != 1 & demo_race_a_p___13 != 1 & demo_race_a_p___14 != 1 & demo_race_a_p___15 != 1 & demo_race_a_p___16 != 1 & demo_race_a_p___17 != 1 & demo_race_a_p___18 != 1 & demo_race_a_p___19 != 1 & demo_race_a_p___20 != 1 & demo_race_a_p___21 != 1 & demo_race_a_p___22 != 1 & demo_race_a_p___23 != 1 & demo_race_a_p___24 != 1 & demo_race_a_p___25 != 1) & demo_ethn_v2 == 1)

#Asian
demographics_followup_abcdmodel %>% 
  filter(demo_race_a_p___10 != 1 & demo_race_a_p___11 != 1 & demo_race_a_p___12 != 1 & demo_race_a_p___13 != 1 & demo_race_a_p___14 != 1 & demo_race_a_p___15 != 1 & demo_race_a_p___16 != 1 & demo_race_a_p___17 != 1 & ( demo_race_a_p___18 == 1 | demo_race_a_p___19 == 1 | demo_race_a_p___20 == 1 | demo_race_a_p___21 == 1 | demo_race_a_p___22 == 1 | demo_race_a_p___23 == 1 | demo_race_a_p___24 == 1) & demo_race_a_p___25 != 1 & demo_ethn_v2 != 1)

#Native American Alaska Native
demographics_followup_abcdmodel %>% 
  filter(demo_race_a_p___10 != 1 & demo_race_a_p___11 != 1 & (demo_race_a_p___12 ==1 | demo_race_a_p___13 == 1) & demo_race_a_p___14 != 1 & demo_race_a_p___15 != 1 & demo_race_a_p___16 != 1 & demo_race_a_p___17 != 1 & demo_race_a_p___18 != 1 & demo_race_a_p___19 != 1 & demo_race_a_p___20 != 1 & demo_race_a_p___21 != 1 & demo_race_a_p___22 != 1 & demo_race_a_p___23 != 1 & demo_race_a_p___24 != 1 & demo_race_a_p___25 != 1 )

demographics_followup_abcdmodel %>% 
  mutate_at(c(12:33), as.numeric) %>% 
  mutate(
    demo_race_asian = case_when((demo_race_a_p___18 == 1 | demo_race_a_p___19 == 1 | demo_race_a_p___20 == 1 | demo_race_a_p___21 == 1 | demo_race_a_p___22 == 1 | demo_race_a_p___23 == 1 | demo_race_a_p___24 == 1) ~ 1,
                            (demo_race_a_p___18 != 1 & demo_race_a_p___19 != 1 & demo_race_a_p___20 != 1 & demo_race_a_p___21 != 1 & demo_race_a_p___22 != 1 & demo_race_a_p___23 != 1 & demo_race_a_p___24 != 1) ~ 0),
         demo_race_native_american_alaskan = case_when((demo_race_a_p___12 ==1 | demo_race_a_p___13 == 1) ~ 1,
                                                       (demo_race_a_p___12 !=1 & demo_race_a_p___13 != 1) ~ 0),
         race_total = rowSums(across(c(demo_race_a_p___10, demo_race_a_p___11, demo_race_a_p___14, demo_race_a_p___15, demo_race_a_p___16, demo_race_a_p___17, demo_race_a_p___25, demo_race_asian, demo_race_native_american_alaskan)), na.rm=T)) %>% 
  filter(race_total > 1)

demographics_followup_abcdmodel %>% 
  filter(demo_race_a_p___10 != 1 & demo_race_a_p___11 != 1 & demo_race_a_p___12 != 1 & demo_race_a_p___13 != 1 & (demo_race_a_p___14 == 1 | demo_race_a_p___15 == 1 | demo_race_a_p___16 == 1 | demo_race_a_p___17 == 1 | demo_race_a_p___25 == 1) & demo_race_a_p___18 != 1 & demo_race_a_p___19 != 1 & demo_race_a_p___20 != 1 & demo_race_a_p___21 != 1 & demo_race_a_p___22 != 1 & demo_race_a_p___23 != 1 & demo_race_a_p___24 != 1)

@@

@@

ggsave(filename="model1_2_overlaid_baseline.png",
                          width=7, height=4, units='in', dpi=300)

```
# Plot of model 1 & 2 prediction overlaid (followup)
```{r}
# overlay model 1 on new predictions in fig 4

@@

ggplot(both_mods_followup, aes(x=truth, y=corrected_pred, group=model, col=model, fill=model)) +
  geom_jitter(alpha=.2) +
  scale_color_manual(values = c("#619B8A", "#856088")) +
  #geom_abline(a=0, b=1, color='#233D4D') +
  #xlim(8, 15) + # 5, 20
 # ylim(8, 15) +
  #geom_smooth(method=lm, color='#233D4D') +
  labs(x = "Scan/Chronological Age", y ="Predicted Age") +
  theme_classic() + 
  theme(text = element_text(size = 14))  
ggsave(filename="model1_2_overlaid_followup.png",
                          width=7, height=4, units='in', dpi=300)

@@

```{r}

@@

@@

# vip
#abcd_model_obj_combat_followup <- fit_workflow_combat_followup$fit$fit$fit

@@

#vip(abcd_model_obj_combat_followup, num_features = 20)
#vi(fit_workflow_combat_followup$fit$fit$fit)

@@

abcd_vi_followup <- left_join(vi(fit_workflow_combat_followup), abcd_vi_renamed)

@@

abcd_vi_dk_followup <- left_join(vi(fit_workflow_combat_followup), abcd_vi_renamed_dk)

@@

ggplot(dk_vi_vol_followup) +
  geom_brain(atlas = dk, position = position_brain(hemi ~ side), aes(fill = Importance))+
  theme_void() +
  scale_fill_gradient(low = '#FDD872', high = '#E76F51') +
  labs(title = "Cortical Volume")
ggsave(filename="abcd_model_dk_vol_importance_followup.png",
                         width=8, height=4, units='in', dpi=300)

@@

ggplot(dk_vi_area_followup) +
  geom_brain(atlas = dk, position = position_brain(hemi ~ side), aes(fill = Importance))+
  theme_void() +
  scale_fill_gradient(low = '#FDD872', high = '#E76F51') +
  labs(title = "Cortical Area")
ggsave(filename="abcd_model_dk_area_importance_followup.png",
                         width=8, height=4, units='in', dpi=300)

@@

ggplot(aseg_vi_followup) +
  geom_brain(atlas = aseg, side="coronal", aes(fill = Importance))+
  theme_void() +
  scale_fill_gradient(low = '#FDD872', high = '#E76F51')
ggsave(filename="abcd_model_aseg_importance_coronal_followup.png",
                          width=7, height=4, units='in', dpi=300)

ggplot(aseg_vi_followup) +
  geom_brain(atlas = aseg, side="sagittal", aes(fill = Importance))+
  theme_void() +
  scale_fill_gradient(low = '#FDD872', high = '#E76F51')
ggsave(filename="abcd_model_aseg_importance_sagittal_followup.png",
                          width=7, height=4, units='in', dpi=300)

@@

# Correlation between BrainAGE at both waves 
```{r}

# correlation for Model 1
# join baseline and follow-up corrected gaps by id
brainage_both_waves <- left_join(brainage_pds_baseline_combat %>% select(src_subject_id, corrected_pred, corrected_gap) %>% rename(baseline_pred = corrected_pred, baseline_gap = corrected_gap), brainage_pds_followup_combat %>% select(src_subject_id, corrected_pred, corrected_gap) %>% rename(followup_pred = corrected_pred, followup_gap = corrected_gap))
